\textbf{EECS 340: Assignment 2}

### 2020-02-03 assignment_2/article.tex
🐛 Correct Problem 1(b1).

@@

According to the defination of $O$-notation, we have:

\begin{gather}
    f(n) = O(f(n)) \nonumber\\
    \exists c, n_{0} > 0 \ \text{ s.t.  $0 \leq f(n) \leq cf(n)$ \ \ \ for $n \geq n_{0}$} \\
    \exists n' > 0 \ \text{ s.t.  $f(n) \geq f(n')$ \ \ \ for $n, n' \geq n_{0}$} \\
    \Rightarrow 0 \leq f(n)+d \leq cf(n) + d \ \ \ \text{for $n \geq n_{0}$}
\end{gather}

Due to \textit{Equation 5}, we may rewrite \textit{Euqation 6} as:

\begin{gather}
    0 \leq f(n)+d \leq (c + \frac{d}{f(n)})f(n) \nonmumber\\
    \Rightarrow 0 \leq f(n)+d \ \leq \ c'f(n) \ \ \ \text{for } \begin{cases}
                    c' = c + \frac{d}{f(n')} \\
                    n, n' \geq n_{0}
                \end{cases}
\end{gather}

Based \textit{Euqation 8}, we may conclude $f(n) + d = O(f(n))$ via direct proof.

>>>>

\textbf{False}

@@

To prove the statement to be valid, we need to show:

\begin{gather}
    0 \leq f(n) + d \leq cf(n)
\end{gather}

For $f(n) = 0$, we cannot find any $c$ which satisfies the above equation since:

\begin{gather}
    O(f(n)) = cf(n) = 0  \nonumber \\
    \Rightarrow 0 \leq 0 + d \leq c(0) \ \ \ \text{for $d > 0$}
\end{gather}

As the equation $0 + d \leq 0$ leads to a contradiction, the statement is invalid.
